### 2017-12-11 submission/supplemental.Rmd
add table s5

**Table S5: **

@@

>>>>

**Table S5: Kruskal-Wallis Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

mock_error_rate_kruskal <- as.data.frame(read_csv("../data/process/tables/mock_error_overall_kruskal_results.csv")) %>% 
  mutate_at(vars(statistic), funs(round(., digits = 2))) %>% 
  mutate_at(vars(pvalue:bh), funs(format(., scientific = TRUE, digits = 2, nsmall = 2))) %>% 
  filter(sub_sample_level > 500)

colnames(mock_error_rate_kruskal) <- c("Rank Sum Statistic", "DF", "P-value", "BH", "Cycle", "Sub-Sample Depth")

kable(mock_error_rate_kruskal, format = "markdown", align = 'c', padding = 2)
```
